### 2020-04-25 final_report/data.tex
add hardware information about hypatia nodes

With grid search in high-dimensional domain clearly intractable, we
selected uniform pseudo-random sampling to generate large amounts of feature
configurations that we consider to be independent and unbiased. For evaluation
of the expensive MC TBR model, we utilise parallelisation offered by
the HPC infrastructure available at UCL computing facilities. To this end, we
designed and implemented the Approximate TBR Evaluator---a Python software package capable of
sequential evaluation of the multi-threaded OpenMC simulation on batches of
previously generated points in the feature space.
We deployed ATE at the UCL Hypatia cluster RCIF partition, which consists of
4~homogeneous nodes, each containing 40 cores. We completed three data
generation runs, which are summarised in~\cref{tbl:sampling-runs}.

>>>>

With grid search in high-dimensional domain clearly intractable, we
selected uniform pseudo-random sampling to generate large amounts of feature
configurations that we consider to be independent and unbiased. For evaluation
of the expensive MC TBR model, we utilise parallelisation offered by
the HPC infrastructure available at UCL computing facilities. To this end, we
designed and implemented the Approximate TBR Evaluator---a Python software package capable of
sequential evaluation of the multi-threaded OpenMC simulation on batches of
previously generated points in the feature space.
We deployed ATE at the UCL Hypatia cluster RCIF partition, which consists of
4~homogeneous nodes, each containing 40 cores.\footnote{Hypatia RCIF nodes use
Intel\textsuperscript{\textregistered} Xeon\textsuperscript{\textregistered}
Gold 6148 CPU with frequency 2.40~GHz and 376 GB RAM.} We completed three data
generation runs, which are summarised in~\cref{tbl:sampling-runs}.
